Towards human SuperEEG

### 2018-10-03 paper/main.tex
backing up current progress (made it through abstract + intro)
checking in more changes (reverted and revamped intro, now getting into approach)

\documentclass[12pt]{article}

@@

\title{Towards human Super EEG}

@@

\begin{abstract}
A growing body of literature over the past several decades reports that the dynamic correlational structure of functional neuroimaging data may be used to predict which moment of movie or story an individual is experiencing, identify which person's brain a recording came from, and identify the task a person is performing.  However, our structural (anatomical) connectome is roughly static for the duration of typical neuroimaging experiments.  How might these notions of dynamic functional connectomes versus static structural connectomes be reconciled?  We use two human electrocorticographic (ECoG) datasets to ask: to what extent can we use a static connectome model (trained using within versus across subject data, and within versus across task data) to explain dynamic full-brain activity patterns?  Given a fixed connectome model, and given recordings from a subset of brain locations, we test how reliably can one infer activity patterns throughout the rest of the brain.  Our model-based approach, termed \textit{SuperEEG}\footnote{The term ``Super EEG'' was
coined by Robert J. Sawyer in his popular science fiction novel
\textit{The Terminal Experiment}~\cite{Sawy95}}, is in itself useful for inferring full-brain activity patterns (at millimeter-scale spatial resolutions and millisecond-scale temporal resolutions) from ECoG recordings from a limited set of brain locations.  For both datasets, we found that full-brain activity patterns can be best explained using connectomes from \textit{other} people who performed a shared task.\\

\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
\end{abstract}

Are our brain's networks static or dynamic?  And to what extent are the network properties of our brains stable across people and tasks?  One body of work suggests that our brain's \textit{functional} networks are dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g., ][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the gross anatomical structure of our brains changes meaningfully over the course of years as our brains develop, on the timescales of typical neuroimaging experiments (i.e., hours to days) our anatomical networks are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many aspects of brain anatomy, including white matter structure, is largely preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}  There are several possible means of reconciling this apparent contradiction between dynamic person- and task-specific functional networks versus stable anatomical networks.  For example, relatively small magnitude anatomical differences across people may be reflected in reliable functional connectivity differences.  Along these lines, one recent study found that diffusion tensor imaging (DTI) structural data is similar across people, but may be used to predict person-specific resting state functional connectivity data~\citep{BeckEtal18}.  Another (potentially complementary) possibility is that our functional networks are constrained by anatomy, but nevertheless exhibit rapid task-dependent changes~\citep[e.g., ][]{SporBetz16}.

Here we take a model-based approach to studying whether high spatiotemporal resolution activity patterns throughout the human brain may be explained by a static connectome model that is shared across people and tasks.  Specifically, we trained a model to take in recordings from a subset of brain locations, and then predict activity patterns during the same interval, but at \textit{other} locations that were held out from the model.  Our model, based
on Gaussian process regression, relies on three assumptions (each of which we test).  First, we assume that functional correlations are stable over time and across tasks.  Second, we assume that some of the correlational structure of people's brain activity is similar across individuals.  Third, we resolve
ambiguities in the data by assuming that neural activity from
nearby sources will tend to be similar, all else being equal.  After fitting the model to an ECoG dataset, one
can then ask (for a held-out individual's brain): given what we
know about the correlational structure of \textit{other} people's brains,
and given the recordings we made from electrodes implanted in this
person's brain, how would those recordings most likely have looked
at \textit{other} locations throughout this person's brain?  We named our general approach \textit{SuperEEG} because the trained model provides a means of inferring full-brain activity patterns at high spatiotemporal resolutions, using ECoG recordings taken from a limited set of brain locations.

We tested the SuperEEG approach using two large ECoG datasets. Dataset 1 comprises multi-hour recordings from 6876 electrodes taken across several recording sessions as 88 neurosurgical patients studied random word lists periodically throughout their day~\cite{SedeEtal03, SedeEtal07a,
  SedeEtal07b, MannEtal11, MannEtal12}.  Dataset 2 comprises recordings from XXX electrodes taken as XXX patients performed a series of two memory tasks~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  In both datasets, 
  we compared the predictions made using models trained across people to predictions made using within-person data.  We found that models that incorporate data from other patients yield far more reliable predictions about an individual patient's brain activity patterns than models trained solely on that individual's data.  This indicates that at least some functional correlations are common across people.  We also used Dataset 2 to compare predictions made using data from within task, across task, or combining within and across task data.  We found that all three approaches yielded reliable predictions, but the within task predictions were the most accurate.  This indicates that some aspects of our functional connectomes are common across tasks, whereas other aspects are task-specific.  Finally, all of the models we trained (within and across patients and tasks) assumed a static connectome and yielded above-chance accuracy.  This indicates that despite moment-by-moment fluctuations in the functional connectome, at least some aspects of our connectome appear to be stable over the course of several hours.

\section*{Approach}
The SuperEEG approach to inferring high temporal resolution full-brain activity patterns is outlined and summarized in
Figure~\ref{fig:methods}. We describe (in this section) and evaluate
(in \textit{Results}) our approach using a two large previously collected
dataset comprising multi-session intracranial recordings.  The first dataset was taken from
6876 electrodes implanted in the brains of 88 epilepsy
patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
  MannEtal12}.  We first applied a fourth order Butterworth notch filter to remove
60 Hz ($\pm$ .5 Hz) line noise.  We then excluded any electrodes that
showed putative epileptiform activity.  Specifically, we excluded from
further analysis any electrode that exhibited an average kurtosis of
10 or greater across all of that patient's recording sessions.  We
also excluded any patients with fewer than 2 electrodes that passed
this criteria, as the Super EEG algorithm requires measuring
correlations between 2 or more electrodes from each patient.
Altogether this yielded clean recordings from 4168 electrodes
implanted throughout the brains of 67 patients (Fig.~\ref{fig:methods}A). For the purposes of comparing task-specific contributions to reconstruction accuracy, we limited our analyses in the second dataset to patients that participated in two free recall experiments.  Applying the same kurtosis thresholding yielded clean recordings from 24 patients and 2975 electrodes for the second dataset. Each individual patient contributes
electrodes from a limited set of brain locations, which we localized
in a common space (MNI152); an example patient's 54 electrodes that
passed the predefined kurtosis test are highlighted in black and red.

@@

Let $\alpha$ be the set of indices of patient $s$'s electrode locations in
$\bar{R}$, and let $\beta$ be the set of indices of all other
locations in $\bar{R}$. In other words, $\beta$ reflects the locations
in $\bar{R}$ where we did not observe a recording for patient $s$
(these are the recording locations we will want to fill in using Super EEG).
We can sub-divide $\hat{K}$ as follows:

@@

\begin{align}
Y_{s,k,\beta} &= ((\hat{K}_{\beta,\alpha}\cdot\hat{K}_{\alpha,\alpha}^{-1})\cdot Y_{s,k,\alpha}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
\end{align}
This equation is the foundation of the Super EEG algorithm.  Whereas
we observe the recordings only at the locations in $\alpha$,
Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
at all locations in $\beta$, which we can define \textit{a priori} to
include any locations we wish, throughout the brain.  This yields estimates of
the time-varying voltages at \textit{every} location in $\bar{R}$.

@@

The Super EEG algorithm described above and in
Figure~\ref{fig:methods} allows us to estimate (up to a constant
scaling factor) LFPs for each patient at all arbitrarily chosen
locations in the set $\bar{R}$, \textit{even if we did not record that
  patient's brain at all of those locations}.

\section*{Results}
To test the accuracy with which the Super EEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
dataset in turn and treated it as unobserved. We then asked: how
closely did each of the Super EEG-reconstructed LFPs match the
observed data?  We sought to evaluate both the overall reconstruction
accuracy as well as how reconstruction accuracy varied as a function
of implantation location.

We first examined raw LFP traces and their associated Super
EEG-derived reconstructions.  Figure~\ref{fig:recon}A displays the
LFP from the red electrode in Figure~\ref{fig:methods}A, and its
associated reconstruction, during a 5~s time window during one of the
patient's 6 recording sessions.  Figure~\ref{fig:recon}B displays a 2D
histogram of the observed versus reconstructed voltages for every
sample across 14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the Super EEG
algorithm recovered the recordings from this electrode well, we sought to
quantify the algorithm's performance across the full dataset.

@@

We obtained a single correlation coefficient for each electrode
location in $\bar{R}$, reflecting how well the Super EEG algorithm was
able to recover the recording at that location by incorporating data across patients (Across shown in black, see Fig.~\ref{fig:corrmap}A). We also reconstructed activity for each electrode using a model trained on the remaining electrodes from only that patient, to account for reconstruction accuracy attributed to volume conductance alone (Within shown in gray, see Fig.~\ref{fig:corrmap}A). For the first dataset, we compared these two distributions of correlation coefficients (paired $t$-test
between $z$-transformed mean correlation coefficients by patient:
$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar results (paired $t$-test
between $z$-transformed mean correlation coefficients by patient: $t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially conservative
test, given that the Super EEG reconstructions exclude (from the
correlation matrix estimates) all data from the patient whose data is
being reconstructed.  Furthermore, we also replicated this finding for each independent experiment within dataset 2 (Fig. S3 (paired $t$-test
between $z$-transformed mean correlation coefficients by patient for experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).  That the Super EEG-derived correlations were reliably
stronger than these correlations obtained using a volume conductance null model is exciting
for two reasons.  First, it implies that distant electrodes provide
additional predictive power to the data reconstructions beyond the
information contained in nearby electrodes.  Second, it implies that
the spatial correlations driving the Super EEG algorithm are, to some
extent, shared across people.

@@

In addition to exploring how reconstruction quality varies with
location, we also wondered whether there might be effects of electrode
placements on reconstruction quality.  For example, are there
particular implantation locations that yield especially high
reconstruction accuracies at other locations throughout the brain? To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location. The resulting maps highlight the locations of implanted electrodes from patients whose
reconstructions were especially accurate  (Fig.~\ref{fig:informap}A and B). We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations in dark red might therefore be good candidate
implantation targets for neurosurgeons and neurologists who wish to
use Super EEG to reconstruct full-brain electrophysiological signals.
The above findings, that one can infer brain activity throughout a person's brain 
using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.

@@

\section*{Discussion}
%DISCUSSION POINTS
%recap main approach
Super EEG infers full-brain activity patterns by leveraging
correlations in those patterns of brain activity within and across people.  Although
the approach may, in principle, be used to infer brain activity
\textit{anywhere} in the brain, the inferences perform slightly better for
regions with dense electrode sampling across patients.  (Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
are included in the inference procedure, this suggests that reconstruction accuracy should improve.

%why does it work?  redundancy of brain
A fundamental assumption of the Super EEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal17}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that Super EEG relies on are
violated, how can the Super EEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g.\ of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
Super EEG approach that leverage resting state fMRI or structural data
[e.g. diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g.\ informed
by structural MRI scans) may improve the predictive performance of the
approach.

%This technique relies on recordings from many patients performing the
%same basic cognitive task.  To what extent do these findings
%generalize across studies?  For example, could one combine recordings
%from several studies to improve our ability to reconstruct neural
%activity?
One potential limitation of the Super EEG approach is that the above
assumption of covariance stability across people may be violated even
more if different patients are performing different cognitive tasks.
To understand of the extent to which the current findings generalize across
cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks. Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
matrix.  Or, using a more sophisticated approach, one could create a
hierarchical model whereby each task-specific covariance matrix was
modeled as a perturbation of a ``global'' task-unspecific covariance
matrix (which could in turn be informed by fMRI or DTI data).
% Alternatively, if the covariance matrix is stable across tasks, this would
% suggest that recordings from multiple studies could be combined to
% improve the overall reconstruction accuracy.

A second potential limitation of the Super EEG approach is that it
does not provide a natural means of estimating the precise timing of
single-neuron action potentials.  Prior work has shown that gamma band
and broadband activity in the LFP may be used to estimate the firing
rates of neurons that underly the population contributing to the
LFP~\cite{MannEtal09}.  Because Super EEG reconstructs LFPs throughout
the brain, one could in principle use gamma or broadband power in the
reconstructed signals to estimate the corresponding firing rates
(though not the timings of individual action potentials).

>>>>

\documentclass[11pt]{article}

@@

\title{Towards human SuperEEG}

@@

\begin{abstract}
  Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
    Robert J. Sawyer in his popular science fiction novel \textit{The
      Terminal Experiment}~\cite{Sawy95}} entails measuring ongoing
  neural activity with perfect precision and at arbitrarily high
  spatiotemporal resolution.  Although true SuperEEG is impossible
  using existing methods, here we present a model-based method for
  \textit{inferring} neural activity at millimeter-scale spatial
  resolutions and millisecond-scale temporal resolutions using
  standard human intracranial recordings.  Our approach assumes that
  different people's brains exhibit similar spatial correlations, and
  that (all else being equal) neural activity at nearby locations will
  tend to be similar.  One can then ask, for an arbitrary individual's
  brain: given recordings from a limited set of locations in that
  individual's brain, along with the observed spatial correlations in
  other people's recordings, what would recordings most likely have
  looked like at \textit{other} locations in that individual's brain?
%\\
%\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
%local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
\end{abstract}

\section*{Introduction}
Modern human brain recording techniques are fraught with
compromise~\citep{SejnEtal14}.  Commonly used approaches include
functional magnetic resonance imaging (fMRI), scalp
electroencephalography (EEG), and magnetoencephalography (MEG).  For
each of these techniques, neuroscientists and electrophysiologists
must choose to optimize spatial resolution at the cost of temporal
resolution (e.g.\ as in fMRI) or temporal resolution at the cost of
spatial resolution (e.g.\ as in EEG and MEG).  A less widely used
approach (due to requiring work with neurosurgical patients) is to
record from electrodes implanted directly onto the cortical surface
(electrocorticography; ECoG) or into deep brain structures
(intracranial EEG; iEEG).  However, these intracranial approaches also
require compromise: the high temporal and spatial resolutions of
intracranial recordings comes at the cost of substantially reduced
brain coverage, since safety considerations limit the number of
electrodes one may implant in a given patient's brain.  Further, the
locations of implanted electrodes are determined by clinical, rather
than research, needs.

%Beamforming: huge advance for scalp recordings, but the inverse
%problem is fundamentally ambiguous.  This limits the precision with
%which one can measure activity from deep brain structures.
An increasingly popular approach is to improve the effective spatial
resolution of MEG or scalp EEG data by using a geometric approach
called \textit{beamforming} to solve the biomagnetic or bioelectrical
inverse problem~\cite{Sarv87}.  This approach entails using detailed
brain conductance models (often informed by high spatial resolution
anatomical MRI images) along with the known sensor placements
(localized precisely in 3D space) to reconstruct brain signals
originating from theoretical point sources deep in the brain (and far
from the sensors).  Traditional beamforming approaches must overcome
two obstacles.  First, the inverse problem beamforming seeks to solve
has infinitely many solutions.  Researchers have made traction towards
constraining the solution space by assuming that signal-generating
sources are localized on a regularly spaced grid spanning the brain
and that individual sources are small relative to their distances to
the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
some ways much more serious, obstacle is that the magnetic fields
produced by external (noise) sources are substantially stronger than
those produced by the neuronal changes being sought (i.e.\ at deep
structures, as measured by sensors at the scalp).  This means that
obtaining adequate signal quality often requires averaging the
measured responses over tens to hundreds of responses or trials
(e.g. see review by~\cite{HillEtal05}).

Another approach to obtaining high spatial and temporal resolution
neural data has been to collect fMRI and EEG data simultaneously.
Simultaneous fMRI-EEG has the potential to balance the high spatial
resolution of fMRI with the high temporal resolution of scalp EEG,
thereby, in theory, providing the best of both worlds.  In practice,
however, the signal quality of both recordings suffers substantially
when the two techniques are applied simultaneously (e.g. see review
by~\cite{HustEtal12}).  In addition, the experimental designs that are
ideally suited to each technique individually are somewhat at odds.
For example, fMRI experiments typically lock stimulus presentation
events to the regularly spaced image acquisition time (TR), which
maximizes the number of post-stimulus samples.  By contrast, EEG
experiments typically employ jittered stimulus presentation times to
maximize the experimentalist's ability to distinguish electrical brain
activity from external noise sources such as from 60 Hz alternating
current power sources.

%Direct intracranial recordings are the gold standard method for
%measuring activity from deep brain structures in both humans and
%animals.
%However, one can only implant a limited number of electrodes in a
%given person's brain.  This begs the question: what can we infer
%about the activity exhibited by the rest of that person's brain,
%given what we learn from recordings taken from \textit{other people's
%brains}?
The current ``gold standard'' for precisely localizing signals and
sampling at high temporal resolution is to take (ECoG or iEEG)
recordings from implanted electrodes (but from a limited set of
locations in any given brain).  This begs the following question: what
can we infer about the activity exhibited by the rest of a person's
brain, given what we learn from the limited intracranial recordings we
have from their brain and additional recordings taken from
\textit{other} people's brains?  Here we develop an approach, which we
call \textit{SuperEEG}, based on Gaussian process
regression~\cite{Rasm06}.  SuperEEG entails using data from multiple
people to estimate activity patterns at arbitrary locations in each
person's brain (i.e., independent of their electrode placements).  We
test SuperEEG approach using two large datasets of intracranial
recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
  MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  We show
that the SuperEEG algorithm recovers signals well from electrodes that
were held out of the training dataset.  We also examine the factors
that influence how accurately activity may be estimated (recovered),
which may have important implications for electrode design and
placement in neurosurgical applications.

\section*{Approach}
The SuperEEG approach to inferring high temporal resolution full-brain
activity patterns is outlined and summarized in
Figure~\ref{fig:methods}. We describe (in this section) and evaluate
(in \textit{Results}) our approach using a two large previously
collected dataset comprising multi-session intracranial recordings.
Dataset 1 comprises multi-session recordings taken from 6876
electrodes implanted in the brains of 88 epilepsy
patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
  MannEtal12}.  Each recording session lasted from XXX--XXX hours, and
includes data recorded roughly from when the patients woke up each
morning, to before they went to sleep at the end of each day.  In
addition to typical bed-ridden hospital patient activities (e.g.,
lying in bed, reading, watching television, using personal electronic
devices, listening to music, visiting with family and friends, etc.),
the patients also performed a variety of experimental cognitive tasks
throughout their day (primarily list-learning memory tasks).  For the
purposes of the Dataset 1 analyses presented here, we aggregated all
data across each recording session, ignoring the particular activities
or tasks the patients were performing at any given moment.  We used
Dataset 1 to develop and debug our main SuperEEG approach, and to
examine the extent to which SuperEEG might be able to generate
task-general predictions.  Dataset 2 comprised multi-session
recordings from XXX electrodes implanted in the brains of XXX epilepsy
patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Whereas
Dataset 1 included recordings taken during a wide variety of
behaviors, Dataset 2 included recordings taken as each patient
performed each of two memory tasks: a random word list free recall
task and a categorized word list free recall task.  We used Dataset 2
to further examine the ability of SuperEEG to generalize its
predictions within versus across tasks.

\textbf{JRM STOPPED HERE}

The first dataset was taken from 6876 electrodes implanted in the
brains of 88 epilepsy patients~\cite{SedeEtal03, SedeEtal07a,
  SedeEtal07b, MannEtal11, MannEtal12}.  We first applied a fourth
order Butterworth notch filter to remove 60 Hz ($\pm$ .5 Hz) line
noise.  We then excluded any electrodes that showed putative
epileptiform activity.  Specifically, we excluded from further
analysis any electrode that exhibited an average kurtosis of 10 or
greater across all of that patient's recording sessions.  We also
excluded any patients with fewer than 2 electrodes that passed this
criteria, as the SuperEEG algorithm requires measuring correlations
between 2 or more electrodes from each patient.  Altogether this
yielded clean recordings from 4168 electrodes implanted throughout the
brains of 67 patients (Fig.~\ref{fig:methods}A). For the purposes of
comparing task-specific contributions to reconstruction accuracy, we
limited our analyses in the second dataset to patients that
participated in two free recall experiments.  Applying the same
kurtosis thresholding yielded clean recordings from 24 patients and
2975 electrodes for the second dataset. Each individual patient
contributes electrodes from a limited set of brain locations, which we
localized in a common space (MNI152); an example patient's 54
electrodes that passed the predefined kurtosis test are highlighted in
black and red.

@@

Let $\alpha$ be the set of indices of patient $s$'s electrode locations in
$\bar{R}$, and let $\beta$ be the set of indices of all other
locations in $\bar{R}$. In other words, $\beta$ reflects the locations
in $\bar{R}$ where we did not observe a recording for patient $s$
(these are the recording locations we will want to fill in using SuperEEG).
We can sub-divide $\hat{K}$ as follows:

@@

\begin{align}
Y_{s,k,\beta} &= ((\hat{K}_{\beta,\alpha}\cdot\hat{K}_{\alpha,\alpha}^{-1})\cdot Y_{s,k,\alpha}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
\end{align}
This equation is the foundation of the SuperEEG algorithm.  Whereas
we observe the recordings only at the locations in $\alpha$,
Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
at all locations in $\beta$, which we can define \textit{a priori} to
include any locations we wish, throughout the brain.  This yields estimates of
the time-varying voltages at \textit{every} location in $\bar{R}$.

@@

The SuperEEG algorithm described above and in
Figure~\ref{fig:methods} allows us to estimate (up to a constant
scaling factor) LFPs for each patient at all arbitrarily chosen
locations in the set $\bar{R}$, \textit{even if we did not record that
  patient's brain at all of those locations}.

\section*{Results}
To test the accuracy with which the SuperEEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
dataset in turn and treated it as unobserved. We then asked: how
closely did each of the SuperEEG-reconstructed LFPs match the
observed data?  We sought to evaluate both the overall reconstruction
accuracy as well as how reconstruction accuracy varied as a function
of implantation location.

We first examined raw LFP traces and their associated Super
EEG-derived reconstructions.  Figure~\ref{fig:recon}A displays the
LFP from the red electrode in Figure~\ref{fig:methods}A, and its
associated reconstruction, during a 5~s time window during one of the
patient's 6 recording sessions.  Figure~\ref{fig:recon}B displays a 2D
histogram of the observed versus reconstructed voltages for every
sample across 14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought to
quantify the algorithm's performance across the full dataset.

@@

We obtained a single correlation coefficient for each electrode
location in $\bar{R}$, reflecting how well the SuperEEG algorithm was
able to recover the recording at that location by incorporating data across patients (Across shown in black, see Fig.~\ref{fig:corrmap}A). We also reconstructed activity for each electrode using a model trained on the remaining electrodes from only that patient, to account for reconstruction accuracy attributed to volume conductance alone (Within shown in gray, see Fig.~\ref{fig:corrmap}A). For the first dataset, we compared these two distributions of correlation coefficients (paired $t$-test
between $z$-transformed mean correlation coefficients by patient:
$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar results (paired $t$-test
between $z$-transformed mean correlation coefficients by patient: $t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially conservative
test, given that the SuperEEG reconstructions exclude (from the
correlation matrix estimates) all data from the patient whose data is
being reconstructed.  Furthermore, we also replicated this finding for each independent experiment within dataset 2 (Fig. S3 (paired $t$-test
between $z$-transformed mean correlation coefficients by patient for experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).  That the SuperEEG-derived correlations were reliably
stronger than these correlations obtained using a volume conductance null model is exciting
for two reasons.  First, it implies that distant electrodes provide
additional predictive power to the data reconstructions beyond the
information contained in nearby electrodes.  Second, it implies that
the spatial correlations driving the SuperEEG algorithm are, to some
extent, shared across people.

@@

In addition to exploring how reconstruction quality varies with
location, we also wondered whether there might be effects of electrode
placements on reconstruction quality.  For example, are there
particular implantation locations that yield especially high
reconstruction accuracies at other locations throughout the brain? To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location. The resulting maps highlight the locations of implanted electrodes from patients whose
reconstructions were especially accurate  (Fig.~\ref{fig:informap}A and B). We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations in dark red might therefore be good candidate
implantation targets for neurosurgeons and neurologists who wish to
use SuperEEG to reconstruct full-brain electrophysiological signals.
The above findings, that one can infer brain activity throughout a person's brain 
using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.

@@

\section*{Discussion}
%DISCUSSION POINTS
%recap main approach
SuperEEG infers full-brain activity patterns by leveraging
correlations in those patterns of brain activity within and across people.  Although
the approach may, in principle, be used to infer brain activity
\textit{anywhere} in the brain, the inferences perform slightly better for
regions with dense electrode sampling across patients.  (Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
are included in the inference procedure, this suggests that reconstruction accuracy should improve.

%why does it work?  redundancy of brain
A fundamental assumption of the SuperEEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal17}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that SuperEEG relies on are
violated, how can the SuperEEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g.\ of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
SuperEEG approach that leverage resting state fMRI or structural data
[e.g. diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g.\ informed
by structural MRI scans) may improve the predictive performance of the
approach.

%This technique relies on recordings from many patients performing the
%same basic cognitive task.  To what extent do these findings
%generalize across studies?  For example, could one combine recordings
%from several studies to improve our ability to reconstruct neural
%activity?
One potential limitation of the SuperEEG approach is that the above
assumption of covariance stability across people may be violated even
more if different patients are performing different cognitive tasks.
To understand of the extent to which the current findings generalize across
cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks. Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
matrix.  Or, using a more sophisticated approach, one could create a
hierarchical model whereby each task-specific covariance matrix was
modeled as a perturbation of a ``global'' task-unspecific covariance
matrix (which could in turn be informed by fMRI or DTI data).
% Alternatively, if the covariance matrix is stable across tasks, this would
% suggest that recordings from multiple studies could be combined to
% improve the overall reconstruction accuracy.

A second potential limitation of the SuperEEG approach is that it
does not provide a natural means of estimating the precise timing of
single-neuron action potentials.  Prior work has shown that gamma band
and broadband activity in the LFP may be used to estimate the firing
rates of neurons that underly the population contributing to the
LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
the brain, one could in principle use gamma or broadband power in the
reconstructed signals to estimate the corresponding firing rates
(though not the timings of individual action potentials).
